---
title: "SIGUE, JP-FA4"
author: "Sigue, John Patrick A."
date: "2025-02-25"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 80), tidy = TRUE)
```

## A geospatial analysis system has four sensors supplying images. The percentage of images supplied by each sensor and the percentage of images relevant to a query are shown in the following table.

```{r}
images <- data.frame(sensor = 1:4, Supplied = c(0.15, 0.20, 0.25, 0.40), Relevant = c(0.50, 0.60, 0.80, 0.85))
images
```

### What is the overall percentage of relevant images?

\*R = Relevant, S = Supplied

$$ P(R) = P(R \vert S_1) \cdot P(S_1) + P(R \vert S_2) \cdot P(S_2) + P(R \vert S_3) \cdot P(S_3) + P(R\vert S_4)\cdot P(S_4) $$

```{r}
prob_rel <- sum(images$Supplied * images$Relevant)

cat("The overall percentage of relevant images is ", prob_rel * 100, "%.", sep = "")
```

## A fair coin is tossed twice. Let $E_1$ be the event that both tosses have the same outcome, that is $E_1 = (HH, TT)$. Let $E_2$ be the event that the first toss is a head, that is, $E_2 = (HH, HT)$. Let $E_3$ be the event that the second toss is a head, that it, $E_3 = (TH, HH)$. Show that $E_1, E_2, \text{and } E_3$ are pairwise independent but not mutually independent.

### Sample Space

$$S = {HH, HT, TH, TT}$$

Since the coin is fair, each outcome has an equal probability: $$P({HH}) = P({HT}) = P({TH}) = P({TT}) = \frac{1}{4}$$

### Events and Their Probabilities

1. $E_1 = (HH, TT)$
    + $P(E_1) = P(HH) + P(TT) = \frac{1}{4} + \frac{1}{4} = \frac{1}{2}$

2. $E_2 = (HH, HT)$
    + $P(E_2) = P(HH) + P(HT) = \frac{1}{4} + \frac{1}{4} = \frac{1}{2}$
    
3. $E_3 = (TH, HH)$
    + $P(E_3) = P(TH) + P(HH) = \frac{1}{4} + \frac{1}{4} = \frac{1}{2}$
    
### Check for Pairwise Independence
Events $A$ and $B$ are independent if:
$$P(A \cap B) = P(A) P(B)$$


1. $E_1 \text{ and } E_2 \newline E_1 \cap E_2 = \{HH\} \newline  P(E_1 \cap E_2) = P(HH) = \frac{1}{4} \newline P(E_1) P(E_2) = \frac{1}{2} \times \frac{1}{2} = \frac{1}{4}\newline$
Since $P(E_1 \cap E_2) =  P(E_1) P(E_2)$, $E_1 \text{ and } E_2$ are independent.

2. $E_1 \text{ and } E_3 \newline E_1 \cap E_3 = \{HH\} \newline  P(E_1 \cap E_3) = P(HH) = \frac{1}{4} \newline P(E_1) P(E_3) = \frac{1}{2} \times \frac{1}{2} = \frac{1}{4}\newline$
Since $P(E_1 \cap E_3) =  P(E_1) P(E_3)$, $E_1 \text{ and } E_3$ are independent.

3. $E_2 \text{ and } E_3 \newline E_2 \cap E_3 = \{HH\} \newline  P(E_2 \cap E_3) = P(HH) = \frac{1}{4} \newline P(E_2) P(E_3) = \frac{1}{2} \times \frac{1}{2} = \frac{1}{4}\newline$
Since $P(E_2 \cap E_3) =  P(E_2) P(E_3)$, $E_2 \text{ and } E_3$ are independent.

### Check for Mutual Independence
$E_1, E_2, \dotsc , E_k$ are mutually independent if:
$$P(E_{i_1} \cap E_{i_2} \cap \dotsm \cap E_{i_k}) = P(E_{i_1})P(E_{i_2})\dotsm P(E_{i_k})$$

From the sets:
$\newline E_1 \cap E_2 \cap E_3 = \{HH\} \newline P(E_1 \cap E_2 \cap E_3) = P(HH) = \frac{1}{4}$

Calculate $P(E_1)P(E_2)P(E_3)$:
$\newline P(E_1)P(E_2)P(E_3) = \frac{1}{2} \times \frac{1}{2} \times \frac{1}{2} = \frac{1}{8}\newline$

Since $P(E_1 \cap E_2 \cap E_3) \neq P(E_1)P(E_2)P(E_3)$, the events are not mutually independent.