---
title: "SEC1-FAE1-SIGUE,JP-FAE1"
subtitle: "Github: https://github.com/PatrickSigue/APM1110/blob/main/FAE1/SEC1-FAE1-SIGUE%2CJP-FAE1.md"
author: "Sigue, John Patrick A."
date: "2025-02-18"
output: md_document
geometry: margin = 2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A malicious spyware can infect a computer system though the Internet or through email. The spyware comes through the Internet 70% of the time and 30% of the time, it gets in through email. If it enters via the Internet the anti-virus detector will detect it with probability 0.6, and via email, it is detected with probability 0.8.

```{r}
spyware <- data.frame(detected = c(0.6, 0.8), undetected = c(0.4, 0.2),
                      via = c(.70, .30), row.names = c("Internet", "Email"))
spyware
```

### (a) What is the probability that this spyware infects the system?

\*Infect = Undetected

$$
P(I) = P(I \vert Internet) \cdot P(Internet) + P(I \vert Email) \cdot P(Email)
$$

```{r}
prob_infect <- round(.4 * .7 + .2 * .3, 4)

cat("The probability that this spyware infects the system is ", 
    prob_infect * 100, "%", sep = "")
```

### (b) If the spyware is detected, what is the probability that it came through the Internet?

\*P(D) = 1 - P(I)

$$
P(D \vert Internet) = \frac{P(Internet \vert D) \cdot P(Internet)}{P(D)}
$$

```{r}
prob_detect <- 1 - prob_infect
prob_det_int <- round((0.6 * 0.7)/(prob_detect), 4)

cat("The probability that the spyware detected came from the internet is ", 
    prob_det_int * 100, "%", sep = "")
```

## Of the emails you receive 20% are spam on average. Your spam filter is able to detect 90% of them but also misclassifies as spam 15% of the genuine emails.

```{r}
email <- data.frame(correct = c(.90, .85), incorrect = c(.10, .15),
                    recieved = c(.20, .80), row.names = c("Spam", "Genuine"))
email
```

### (a) If an email arrives and is marked spam, what is the probability that it really is spam?

$$
P(S \vert C) = \frac{P(C\vert S)\cdot P(S)}{P(Spam)} \newline
P(Spam) = P(C\vert S)\cdot P(S) + P(I\vert G)\cdot P(G)
$$

```{r}
prob_spam <- round((.90 * .20 + .15 * .8), 4)
prob_spam_c <- round(((.90 * .2)/ prob_spam), 4)

cat("The probability of an email marked spam that is spam is ", prob_spam_c * 100, "%.", sep = "")
```

### (b) If an email arrives and is not marked spam, what is the probability that it is legitimate?

$$
P(G \vert C) = \frac{P(C\vert G)\cdot P(G)}{P(Genuine)} \newline
P(Genuine) = P(C\vert G)\cdot P(G) + P(I\vert S)\cdot P(S)
$$

```{r}
prob_gen <- round((.85 * .80 + .10 * .20), 4)
prob_gen_c <-round(((.85 * .80)/ prob_gen), 4)

cat("The probability of an email marked genuine that is genuine is ", prob_gen_c * 100, "%.", sep = "")
```
