---
title: "SEC-1-FA6-GROUP-1-SIGUE,-JP-FA6"
author: "Sigue, John Patrick A."
date: "2025-03-05"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 75), tidy = TRUE)
```

## Geometric Distribution. Provide an R code for the geometric distribution. The geometric distribution is a probability distribution that models the number of trials required to achieve the first success in a sequence of Bernoulli trials, where each trial has a constant probability of success.

1. Set the probability of success:  p <- 0.2
```{r}
p <- 0.2
```

2. Generate 1000 random variables from the geometric distribution.
```{r}
x <- rgeom(1000, p)
```

3. Calculate some basic statistics: mean_x <- mean(x), var_x <- var(x), sd_x <- sd(x)
```{r}
mean_x <- mean(x)
var_x <- var(x)
sd_x <- sd(x)
```

4. Print the results in item 3 with the following output (string): Number of trials required to achieve first success, Mean (in 2 decimal places), Variance (in 2 decimal places), Standard deviation ( in 2 decimal places)
```{r}
cat("Number of trials required to achieve first success:\n")
cat("Mean:", round(mean_x, 2))
cat("\nVariance:", round(var_x, 2))
cat("\nStandard Deviation:", round(sd_x, 2))
```

5. Plot the histogram of the results.
```{r}
hist(x, main = "Histogram of Trials to First Success", xlab = "Number of Trials", col = "#568203",  xlim = c(0, max(x)+5), xaxt = "n", yaxt = "n")
axis(side = 1, at = seq(0, max(x)+5, by = 5))
axis(side = 2, at = seq(0, 800, by = 100))
```

## Hypergeometric Distribution.  Consider a plant manufacturing IC chips of which 10% are expected to be defective. The chips are packed in boxes for export. Before transportation, a sample is drawn from each box. Estimate the probability that the sample contains more than 10% defectives, when:

1. A sample of 10 is selected from a box of 40
```{r}
q <- 1 #10%
k <- 10 #sample
m <- 40 * .10 #10% of 40 - defective
n <- 40 * .90 #90% of 40 - non defective

ans <- round(phyper(q, m, n, k), 4)
cat("Probability that the sample contains more than 10% defectives: ", ans*100, "%", sep = "")
```

2. A sample of 10 is selected from a box of 5000
```{r}
q <- 1 #10%
k <- 10 #sample
m <- 5000 * .10 #10% of 5000 - defective
n <- 5000 * .90 #90% of 5000 - non defective

ans <- round(phyper(q, m, n, k), 4)
cat("Probability that the sample contains more than 10% defectives: ", ans*100, "%", sep = "")
```